% Chapter Template

\chapter{Introduction} % Main chapter title

\label{Chapter1} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 1. \emph{Introduction}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

% INTRO
\section*{Overview of Project Area}

In the finance credit risk is one of the oldest forms of risk. Credit risk can be defined as one party ``a lender'' trusting another party ``a borrower'' enough that they are happy to give them with money ``some credit'' where they anticipate to be paid back not instantly but after some time interval, the credit risk is the probability or chance that the ``lender'' is never paid back by the ``borrower''. Credit risk has been in existence since lending commenced itself dating back to 1800 B.C., where there is forever a certain amount of precariousness involved in the lending borrowing process \citep{caouette_managing_1998}.


There are many credit risks in the repayment process of lending where the lender may not receive the full payment, the principle, the interest or both. To help mitigate this issue credit risk scoring and modelling have been employed by financial institutions to identify what borrowers are likely to fail paying back their financial obligation \citep{sirirattanaphonkun_default_2012}.

The phrase \textit{credit scoring} is commonly used to define the procedure of assessing the risk of borrower poses of defaulting on their financial agreement \citep{hand_statistical_1997}. The aim of these models is to classify borrowers ``customers of the financial institution'' into to one of two classes: \textit{good} and {bad}. Good and bad can also be referred to as \textit{defaulters} or \textit{non-defaulters/performing}. Customers in the good class are thought to be more likely to pay back their financial agreement. Customers in the bad classes are thought to be unlikely to pay back their financial agreement. 

\textit{Small and Medium-Sized Enterprises} (SME/SMEs) are commonly defined as registered businesses with fewer than 250 employees \citep{ifc_sme_2009}. There is no consistent definition though as it can vary in different countries and across financial institutions. \cite{beck_bank_2008} research indicates that most commercial financial institutions consider the SME sector to be very profitable. Studies also demonstrate that performing SMEs or a strong SME sector is important as it forms the spine of countries economies all around the world, because they are hubs for providing jobs, innovation and growth to the economy \citep{craig_sba-guaranteed_2004}. It is therefore vital from a financial institution profitability point of view that their credit risk models are as accurate as possible and have all the information available to make an informed prediction. It is also vital from a countries economies point of view that this is done so SMEs do not default and people do not lose their jobs. 


Since the financial crisis of 2007-2008 there has been a much greater emphasis on credit scoring for the entire consumer lending process in financial institutions. One of the most common methods of building credit risk models is by using data mining \citep{baesens_50_2009}. One of the benefits to improving the scoring accuracy of a credit model is the significant future savings \citep{west_neural_2000} but also financial institutions are under increasing pressures from global (Bank for International Settlements) e.g. The European Central Bank and national bank e.g. Central bank of Ireland. Since the crisis these regulators police that financial institutions keep better care of their credit scoring systems. Poor performing credit systems can have massive adverse effect on that financial institutions profits, reputation and ability to support the economy.

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Background}

We begin with a high-level overview of SME credit scoring and location data in machine learning.

\subsection{SME Credit Scoring}

Credit scoring, in layman's language is the name given to describe the process of assessing how risky customers and applicants are to default on their financial obligation \citep{hand_statistical_1997}. The goal is to split customers into two classes, 'good' and 'bad'. Customers in the good class are considered likely to repay on their financial obligation while customers in the bad class are likely to default on theirs. In order to make this decision about its customers, financial institutions use information known about the customer and other relevant metrics to identify how risky a customer is. 


Since the financial crisis of 2007-2008 there has been a  much greater emphasis on credit scoring in the consumer lending process in banking. One of the most common methods of building scorecards is by using data mining \citep{baesens_50_2009}. 
\\\\
There are three main stages of a typical credit scorecard development \cite{van_gestel_credit_2009}

\begin{itemize}
	\item Dataset Construction
	\item Modelling
	\item Documentation 
\end{itemize}

This can displayed using this architectural diagram. Insert find diagram.
\\\\
Each stage of this process cannot be left out when completing a industry credit scorecard, however for this research will be focusing particularly on the data construction and modelling stages. The documentation stage is critical for deployment of an industry scorecard but will not be investigated further in this thesis. 

%----------------------------------------------------------------------------------------
%	
%----------------------------------------------------------------------------------------

Since the financial of 2007-2008 there is an even greater emphasis on quality credit scoring. In Ireland it was the property bubble that collapsed causing the banking crisis. 

"Many believe that focusing on lending on the SME sector could play an important role in restoring faith in the banking system and supporting economic growth, according to leading experts"


The primary aim of this research project is to build a quantitative credit scorecard that will identify Small Medium Enterprise (SME) customers who are likely to go into arrears/defaults.


The upheaval in the financial markets that accompanied the 2007-2008 sub-prime
mortgage crisis has emphasised the large proportion of the banking industry based
on consumer lending (Thomas, 2009b). Credit scoring is an important part of the
consumer lending process. It is an endeavour regarded as one of the most popular
application fields for both data mining and operational research techniques (Baesens
et al., 2009). Improving the scoring accuracy of the credit decision by as much as
a fraction of a percent can result in significant future savings (West, 2000). Furthermore,
global (Bank for International Settlements) and national (central banks)
regulators insist that financial institutions keep better track of their credit scoring
systems. The costs of incorrectly classifying a customer can be high, both financially
and in terms of reputation.


\textit{It is an endeavour regarded as one of the most popular
application fields for both data mining and operational research techniques (Baesens
et al., 2009). Improving the scoring accuracy of the credit decision by as much as
a fraction of a percent can result in significant future savings}



\textit{footnotes found in \citep{rocha_status_2011} also very good introduction for references
	According to Ayyagari et al., (2007) SMEs account for more than 60\% of manufacturing employment across 76
	developed and developing economies. 
	Schiffer and Weder (2001), IADB (2004) and Beck et al. (2005, 2006 and 2008) show SMEs perceive access to
	finance and cost of credit to be greater obstacles than large firms and these factors affect their growth.
}

Two thirds of the labour workforce are employed by SMEs with less than 250 employees in countries in \textit{The Organisation for Economic Co-operation and Development} (OECD)\footnote{The OECD's origins date back to 1960, when 18 European countries plus the United States and Canada joined forces to create an organisation dedicated to economic development. Today, our 34 Member countries span the globe, from North and South America to Europe and Asia-Pacific. They include many of the world’s most advanced countries but also emerging countries like Mexico, Chile and Turkey. We also work closely with emerging economies like the People's Republic of China, India and Brazil and developing economies in Africa, Asia, Latin America and the Caribbean. Together, our goal continues to be to build a stronger, cleaner and fairer world. \url{http://www.oecd.org/about/membersandpartners/}} (\cite{beck_bank_2008}; \cite{dietrich_explaining_2012}). In its simplest 

\textit{There  are  numerous  studies  on  credit 
	risk based on financial data of listed companies, which are mostly 
	large  corporations,  but  very  few  studies  utilized  the  data  of  small 
	and  medium  enterprises  (SMEs).  This  could  be  mainly  due  to  the 
	concern of the reliability of the data since large firms listed at the 
	stock  exchanges  are  closely  monitored  by  the  authority  to  ensure 
	that the financial data provide accurate and useful information for 
	investors and shareholders. \citep{sirirattanaphonkun_default_2012}}

\textit{The
	implementation of reliable statistical methods to measure and forecast these probabilities implies the
	consideration of an observation period. In other words, the identification of default events implies mon
	-
	itoring each debtor over time and the identification of a transition from non-default to a default state.
	The obtained statistics are useful for credit institutions in many ways, spanning from the credit ap-
	proval process (for instance to implement cut-off points to screen credit applications), to the establish-
	ment of risk-sensitive pricing, the decision on whether collateral is required or not, the estimation of
	provisioning requirements or impairment losses, and the assessment of capital adequacy.
	\citep{antunes_estimating_2005}}

Studies demonstrate that performing SMEs are vital as they as seen as the spine of countries economies all around the world, because they are hubs for providing jobs, innovation and growth to the economy \citep{craig_sba-guaranteed_2004}.


\textit{For example, we know that during recessions, consumers
	are likely to cut back on luxuries, and thus firms in the consumer durable goods sector
	should see their credit risk increase. \citep{hackbarth_capital_2006}}

This chapter introduces the research topic, the predictiveness of location-based features in \textit{Small Medium Enterprises} SME credit scoring, and how it can potentially can be used to improve credit scoring in financial institutions. The motivation for the research question are discussed with details of its significance. The aims of the thesis along with the research objectives and analytical approach are then stated. The scope and limitation of this research are then described. The chapter concludes with a summary and outlines of this thesis.

\textit{
	http://www.cso.ie/en/surveysandmethodology/multisectoral/businessdemography/
	The CSO Business Demography results for 2012 found that 68% of Irish private sector employees work for an SME. They account for 52% of total employment.
}


\textit{footnotes found in \citep{rocha_status_2011} also very good introduction for references
	According to Ayyagari et al., (2007) SMEs account for more than 60\% of manufacturing employment across 76
	developed and developing economies. 
	Schiffer and Weder (2001), IADB (2004) and Beck et al. (2005, 2006 and 2008) show SMEs perceive access to
	finance and cost of credit to be greater obstacles than large firms and these factors affect their growth.
}


\cite{beck_bank_2008} research indicates that most commercial financial institutions consider the SME sector to be very profitable. 


\cite{anderson_credit_2007} defines \textit{credit risk} as a risk of a customers defaulting on their financial obligation due to the a negative change in their credit worthiness.

Since the financial crisis of 2007-2008 there has been a  much greater emphasis on credit scoring in the consumer lending process in banking. One of the most common methods of building scorecards is by using data mining \citep{baesens_50_2009}. 

Since the financial crisis of 2007-2008 there has been a  much greater emphasis on credit scoring in the consumer lending process in banking.

The most common definition for an SME is a registered business that with less than 250 employees \citep{ifc_sme_2009}, however this definition is not always consistent and can vary from country to country, financial institution to financial institution. 

Studies demonstrate that performing SMEs are vital as they as seen as the spine of countries economies all around the world, because they are hubs for providing jobs, innovation and growth to the economy \citep{craig_sba-guaranteed_2004}.

Worldwide the most common method by regulators for defining businesses as SME are based the number of people they have employed, sales/turnover or/and loan size \cite{ardic_small_2011}.


\cite{beck_bank_2008} research indicates that most commercial financial institutions consider the SME sector to be very profitable.


%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Research Project}

The aim of this research project is to generate macro-economic features and assess their capability in predicting SME customers that will default on  their financial obligation in \subjectname\ in the future.

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Research Objectives}
The primary goal of this research is to assess the predictive capability of macro-economic features in predicting whether or not SMEs will default on their financial obligation. The predictive models built as part of the experiment will include macro-economic features that will be sourced from internal sources in \subjectname\ and open datasets from the Irish Census.

 
The objectives of this research are:

\begin{itemize}
	\item To study the relevant state-of-the-art literature and industry best practices for credit risk scoring, predictive modelling and how macro-economic features are utilised in credit risk modelling.
	
	\item Design and build application to generate, collate and identify macro-economic features that will be assessed for predicting SMEs defaulting.
	
	\item Design experiments to test the hypothesis
	
	\item Use feature selection techniques to identify the most predictive  macro-economic features.
	
	\item Train benchmark predictive model to compare the and evaluate the experiment with.
	
	\item Train a predictive models including macro-economic features to be evaluated against the benchmark model.

	\item Critically assess the results from predictive models including macro-economic features compared to the benchmark model to evaluate if macro-economic features should be included in credit risk models in the future.

	\item Determine what future research could be undertaken in the area to expand on the project.
\end{itemize}
	

%----------------------------------------------------------------------------------------
%	SECTION 5
%----------------------------------------------------------------------------------------
\section{Research Methodology \& Analytical Approach}

The research methodology that will be deployed in this project is empirical evaluation that will involve investigation and experimentation on a large number of macro-economic. These features will be generated based on customer transactional spending behaviour, default trends over disparate banking credit products (Personal Loans, Homeloans, SMEs) and Census data(Employment levels, Education levels, and Occupation Type).   

The experiment in this research undertaken is based on building a prediction model that is able to accurately predict if SME customers will default or not default in the future. As part of the experiment macro-economic features are evaluated to ascertain if any are accurately able to predict arrears. Building prediction models and evaluating the prediction power of features are common practices in Data Mining.

Data mining is used to explain historic events and forecast future events by applying data analysis. Data mining is commonly used for identify trends that are not obvious. 

In this experiment were are trying to investigate the relationship between good and bad SME customers by macro-economic features by region to see if there are any relationships from the past that could be used to predict the future. It not be feasible to investigate all these relationships manually. Data mining gives you a methodology which is supported by data analysis and experiments. 

Data mining techniques for measuring the importance of features and evaluating the performance of prediction models will be used throughout the empirical evaluation of this project. Many tests will be carried out to try and derive interesting insights from the macro-economic features relationship with SME customer default behaviour.

%----------------------------------------------------------------------------------------
%	SECTION 6
%----------------------------------------------------------------------------------------
\section{Scope and Limitations}
The scope of this project is to build a prediction model in \subjectname\ for SMEs which utilises macro-economic features by geographic regions (Electoral Division and Local Authority) in the Republic of Ireland. The aim of the experiment is to evaluate the predictiveness of these macro-economic features and evaluate if they should be included in industry credit risk models in \subjectname\ in the future.

SMEs included in this project will only be taken from one of the accounting systems in \subjectname. Macro-economic features for this experiment will be generated from customer transactional spending behaviour, default trends over disparate banking credit products (Personal Loans, Homeloans, SMEs) and Census data(Employment levels, Education levels, and Occupation Type). 

As part of the experiment a benchmark prediction model will be trained using features that were selected to be in a SME credit risk model in the past. Further prediction models will be built using the features from the benchmark model and the macro-economic features generated as part of this research. Prediction models using macro-economic features will be compared and evaluated against the benchmark model. If the models trained using the  macro-economic features perform better than the benchmark model then these features should be considered for inclusion in the SME credit risk model in the future. 



%----------------------------------------------------------------------------------------
%	SECTION 7
%----------------------------------------------------------------------------------------
\section{Outline of the Thesis}
The remainder of this thesis is organised as follows:

\begin{itemize}
	\item Chapter 2
	\item Chapter 3
	\item Chapter 4
	\item Chapter 5
	\item Chapter 6
\end{itemize}

